LAGOS lake depth

### 2021-12-07 figures/01_geometry.Rmd
format fig 3

rsq <- round(broom::glance(lm(dist_viscenter ~ dist_deepest, data = dt))$r.squared, 2)
gg_dist_base <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter)) +
  geom_point(size = 1) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_abline(intercept = 0, slope = 1, linetype = 2, color = "darkgreen", size = 1) +
  annotate("text", x = 2550, y = 430, label = paste0("R^2 == ", rsq), # higher y is up
    parse = TRUE, size = text_size - 0.7) +
  annotate("label", x = 1900, y = 150, # 1800
    label = get_formula(
      lm(dist_viscenter ~ dist_deepest, data = st_drop_geometry(dt))),
    size = text_size - 1.1, fill = "white", label.size = NA) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Distance to \n lake center (m)") +
  theme_opts +
  scale_x_continuous(expand = c(0, 0.01), limits = c(0, 3000)) +
  scale_y_continuous(expand = c(0, 1), limits = c(0, 3000))

@@

rsq <- round(broom::glance(lm(nearshore_slope_mean ~ inlake_slope_pnt, data = test))$r.squared, 2)
gg_slope_base <- ggplot(data = test) +
  geom_point(aes(nearshore_slope_mean, inlake_slope_pnt), size = 1) +
  geom_smooth(aes(nearshore_slope_mean, inlake_slope_pnt), method = "lm", se = FALSE) +
  geom_abline(intercept = 0, slope = 1, linetype = 2, color = "darkgreen", size = 1) +
  geom_rect(xmin = 0.28, xmax = 0.42, ymin = 0, ymax = 0.05,
    alpha = 1, fill = "white") +
  annotate("text", x = 0.34, y = 0.05, label = paste0("R^2 == ", rsq),
    parse = TRUE, size = text_size - 0.7) +
  annotate("label", x = 0.22, y = 0.01,
    label = get_formula(
      lm(inlake_slope_pnt ~ nearshore_slope_mean, data = test)),
    size = text_size - 1.2, fill = "white", label.size = NA, label.padding = unit(0.1, "lines")) +
  xlab("Nearshore slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "") +
  theme_opts +
  scale_x_continuous(expand = c(0, 0.01), limits = c(0, NA)) +
  scale_y_continuous(expand = c(0, 0.01), limits = c(0, NA))

cowplot::plot_grid(
  ggdraw() +
    draw_label("True measures", y = 0.37, hjust = 0, size = 12, angle = 90,  fontface = "bold"),
  cowplot::plot_grid(
    cowplot::plot_grid(
      gg_dist_base,
      gg_slope_base,
      rel_widths = c(1, 0.9)
    ),
    ggdraw() +
      draw_label("Proxy measures", x = 0.45, hjust = 0, size = 12, fontface = "bold"),
    ncol = 1, rel_heights = c(1, 0.1)),
  ncol = 2, rel_widths = c(0.1, 1))
```

>>>>

rsq <- round(broom::glance(lm(dist_viscenter ~ dist_deepest, data = dt))$r.squared, 2)
gg_dist_base <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::filter(dist_deepest < 3200) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter)) +
  geom_point(size = 1) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_abline(intercept = 0, slope = 1, linetype = 2, color = "darkgreen", size = 1) +
  annotate("text", x = 2550, y = 430, label = paste0("italic(R^2) == ", rsq), # higher y is up
    parse = TRUE, size = text_size - 0.7) +
  annotate("label", x = 1900, y = 150, # 1800
    label = get_formula(
      lm(dist_viscenter ~ dist_deepest, data = st_drop_geometry(dt))),
    size = text_size - 1.1, fill = "white", label.size = NA) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Distance to \n lake center (m)") +
  theme_opts +
  scale_x_continuous(expand = c(0, 0.01), limits = c(0, 3000)) +
  scale_y_continuous(expand = c(0, 1), limits = c(0, 3000))

@@

rsq <- round(broom::glance(lm(nearshore_slope_mean ~ inlake_slope_pnt, data = test))$r.squared, 2)
gg_slope_base <- ggplot(data = test) +
  geom_point(aes(nearshore_slope_mean, inlake_slope_pnt), size = 1) +
  geom_smooth(aes(nearshore_slope_mean, inlake_slope_pnt), method = "lm", se = FALSE) +
  geom_abline(intercept = 0, slope = 1, linetype = 2, color = "darkgreen", size = 1) +
  geom_rect(xmin = 0.28, xmax = 0.42, ymin = 0, ymax = 0.05,
    alpha = 1, fill = "white") +
  annotate("text", x = 0.34, y = 0.05, label = paste0("italic(R^2) == ", rsq),
    parse = TRUE, size = text_size - 0.7) +
  annotate("label", x = 0.22, y = 0.01,
    label = get_formula(
      lm(inlake_slope_pnt ~ nearshore_slope_mean, data = test)),
    size = text_size - 1.2, fill = "white", label.size = NA, label.padding = unit(0.1, "lines")) +
  xlab("Nearshore slope (mean)") +
  ylab("In-lake slope") +
  labs(color = "") +
  theme_opts +
  scale_x_continuous(expand = c(0, 0.01), limits = c(0, NA)) +
  scale_y_continuous(expand = c(0, 0.01), limits = c(0, NA))

cowplot::plot_grid(
  ggdraw() +
    draw_label("True measures", y = 0.37, hjust = 0, size = 12, angle = 90,  fontface = "bold"),
  cowplot::plot_grid(
    cowplot::plot_grid(
      gg_dist_base,
      gg_slope_base,
      rel_widths = c(1, 0.9),
      labels = c("a", "b"),
      label_x = c(0.08, 0)
    ),
    ggdraw() +
      draw_label("Proxy measures", x = 0.45, hjust = 0, size = 12, fontface = "bold"),
    ncol = 1, rel_heights = c(1, 0.1)),
  ncol = 2, rel_widths = c(0.1, 1))
```
